---
title: "task1"
author: "Milda Pieškutė"
date: '2017 m vasaris 20 d '
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note: when generating data use set.seed(student.code) where student.code is your unique student
code.
1. Model generation and initial analysis
1.1 Generate the following models with sample sizes T = 100 and t ∼ W N(0, 1):
```{r}
set.seed(1512230)
T=100
epsilon<-rnorm(T, 0,1)
```
(1) An AR(3) model with φ1 = 0.6, φ2 = 0.8 and φ3 = −0.7;
```{r}
AR<-arima.sim(list(order = c(3,0,0), ar = c(0.6, 0.8,-0.7)), n = T)
```
(2) An MA(2) model with θ1 = 0.3 and θ2 = 0.6 and mean µ = 2;
```{r}
MA <- 2+0.3*epsilon - 0.6 * c(0, epsilon[-T])
```

(3) An ARMA(1,1) model of the following form: (1 − 0.7L)Yt = 0.7 + (1 − 0.5L)t.
```{r}
arma.sim<-arima.sim(model=list(ar=c(.9,-.2),ma=c(-.7,.1)),n=T)
```

1.2 Plot the sample ACF and PACF for each case - what do they show? What should the theoretical
ACF and PACF show for each of the mentioned processes?

```{r}
par(mfrow = c(2,3))
acf(AR, main = expression(paste(Y[t], " = 0.6", epsilon[t], " + 0.8", epsilon[t-1]," -0.7", epsilon[t-2])))
acf(MA, main = expression(paste(Y[t], " = 2 +0.3 ", epsilon[t], " + 0.6", epsilon[t-1])))
acf(arma.sim, main = expression(paste(Y[t], " = 2 + ", epsilon[t], " + 0.5", epsilon[t-1]))) # Taisyti

pacf(AR, main = expression(paste(Y[t], " = 0.6", epsilon[t], " + 0.8", epsilon[t-1]," -0.7", epsilon[t-2])))
pacf(MA, main = expression(paste(Y[t], " = 2 +0.3 ", epsilon[t], " + 0.6", epsilon[t-1])))
pacf(arma.sim, main = expression(paste(Y[t], " = 2 + ", epsilon[t], " + 0.5", epsilon[t-1]))) # Taisyti

```

1.3 Is the AR(3) process stationary? Is the MA(2) process invertible? What about the ARMA(1,1) process?
Explain your answers.
2. Model estimation
2.1 Estimate the models from the previous part (note: use Arima from the forecast package). What are
the coefficient values of your estimated models? Are they close to the actual values?
2.2 Use the auto.arima function (from the forecast package) to fit the best model for each series. Are the
models and their coefficients estimated by auto.arima the same as the ones used to generate the data?
2.3 Using the estimated models from auto.arima, forecast each model 20 periods ahead. What can you say
about the forecasts, i.e. how do the forecast values change as the forecast period increases?
3. Residual tests
Remember that the previous models were generated with shocks t ∼ W N(0, 1).
3.1 Plot the residuals of your estimated models from the auto.arima. Do their time series plots look like
WN?
3.2 Plot the sample ACF and PACF of your model residuals - do they look like WN?
3.3 Perform the Ljung-Box Test on the residuals of your models. Are the residuals WN in all cases?